\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-09 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   manuscript/main.aux 	modified:   manuscript/main.bbl 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   manuscript/our-cites.bib 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb 	modified:   result_tables/heter_platform_did.tex 	modified:   result_tab

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the study background and the data source. Section \ref{sec:statistical} describes the statistical summary and other relevant information. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} concludes.

@@

Finally, the overall market influence of real estate intermediaries is multi-faceted. Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that an excessive entry of brokers into the market can surpass the optimal allocation, reducing social welfare. This is further evidenced by studies indicating that a surge in broker numbers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}. Additionally, \citet{qu_identifying_2021-1} highlights how broker commissions play a moderating role in disseminating information during transactions, thereby facilitating more efficient home sales. Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.

@@

@@

@@

@@

>>>>

The remainder of the paper proceeds as follows. Section \ref{sec:literature_review} reviews the literature that is related to our research. Section \ref{sec:data} describes the study background and statistical summary. Section \ref{sec:mechanism_design} presents the main result of our finding. Finally, Section \ref{sec:conclusion} contains the discussion and concludes.

@@

Moreover, the overall market influence of real estate intermediaries is multifaceted. Utilizing a model predicated on perfect competition, \citet{williams_agency_1998} illustrates that excessive entry of brokers into the market can surpass the optimal allocation, thereby reducing social welfare. This is corroborated by studies indicating that an increase in the number of brokers can depress house prices and shorten transaction cycles \citep{https://doi.org/10.1002/jae.2891}. Additionally, \citet{qu_identifying_2021-1} highlights the moderating role of broker commissions in disseminating information during transactions, facilitating more efficient home sales. Other related literature includes \citep{doi:10.1080/10527001.2021.2016340, doi:10.1080/10835547.1996.12090852}.

Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017}. Despite the significant attention given to online platforms, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage. Therefore, this paper aims to fill this gap by examining the influence of offline stores associated with online platforms on the real estate market.

@@

In the Appendix Table \ref{tab:} we also report the results of the robustness check of the dynamic model. The results show that the dynamic model

@@

To check the robustness of the entry effect, we also conduct the

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Entry Effect}
      \label{tab:entry_effect_robustness}
      \input{../result_tables/entry_effect_hetero.tex}

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}.
    \end{scriptsize}
  \end{center}
\end{table}

@@

\begin{table}
  \begin{center}
    \begin{scriptsize}
      \caption{Robustness Check of Online Consolidation Effect}
      \label{tab:heter_platform_did}
      \input{../result_tables/heter_platform_did.tex}

    Note: we omit all the control variables in the regression model, and detailed descriptions can be seen from Table \ref{tab:statistical}.
    \end{scriptsize}
  \end{center}
\end{table}

@@

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By HHI Index}
    \label{tab:sylized_fact_hetero_hhi}
    \input{../result_tables/robust_hhi.tex}

\begin{table}[H]
  \begin{center}
    \begin{scriptsize}
    \caption{Robustness Check By Market Maturity Index}
    \label{tab:sylized_fact_hetero_mature}
    \input{../result_tables/robust_mature.tex}
